### 2021-04-21 README.rmd
released on CRAN !

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

@@

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml)
```{r echo=FALSE, results='asis'}
cat(
  badge_github_version(color = "green"),
  badge_cran_release(color = "blue"),
  badge_cran_download(color = "blue", type = "grand-total")
)
```
<!-- badges: end -->

@@

The stable version of `geocmeans` is available on CRAN. You can install it with the command below.
```
install.packages("geocmeans")
```
